Output Summary

### 2023-07-06 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
New output in output-plots: eggs/spawner
New output in output-plots: eggs/female

## Total Eggs vs. Total Spawners

@@

>>>>

## Total Eggs vs. Total Spawners {.tabset .tabset-pills}

### Scatterplot

@@

### Eggs per Spawner

Calculated as total annual egg production divided by the sum of all spawners (regardless of age or sex).
Dashed line shows the time series average for reference.

```{r eggs-per-spawner, fig.width = p4_width, fig.height = p4_height}
# function to create the plot for one population
plot_f = function(j) {
  est = post_summ(post, sub_index("^E_per_Sa[year,pop]$", year = ts_yrs, pop = j))
  plot_tseries(est = est,
               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000)

  # add a time series mean
  mn = mean(est["mean",])
  segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Return Year", "Eggs per Spawner (1000s)")
```

### Eggs per Female

Calculated as total annual egg production divided by the sum of half of all age-4 and age-5 spawners.
Dashed line shows the time series average for reference.

```{r eggs-per-female, fig.width = p4_width, fig.height = p4_height}
# function to calculate eggs-per-female posterior samples
f = function() {
  # extract posterior samples of relevant quantities
  Sa = post_subset(post, "^Sa[", matrix = TRUE)
  E = post_subset(post, "^E[", matrix = TRUE)

  # function to perform derived quantity calculation for each posterior sample
  g = function(i) {

    # format
    Sa_i = array_format(Sa[i,])
    E_i = array_format(E[i,])

    # drop age-3
    no_jacks = Sa_i[,-1,,]

    # add hor and nor
    no_jacks = no_jacks[,,1,] + no_jacks[,,2,]

    # calculate females at age and sum
    females = no_jacks[,1,] * jags_data$Omega[2] + no_jacks[,2,] * jags_data$Omega[3]

    # calculate eggs per female
    as.numeric(E_i/females)
  }

  # apply to each posterior sample
  out = t(sapply(1:nrow(Sa), g))

  # build element indices: the year
  y_ind = rep(1:jags_data$ny, jags_data$nj)

  # build element indices: the population
  j_ind = rep(1:jags_data$nj, each = jags_data$ny)

  # build element names
  colnames(out) = paste0("E_per_Sa_female[", y_ind, ",", j_ind, "]")

  # determine which should be dropped due to NA values
  na_ind = which(!is.na(out[1,]))

  # combine with remainder of posterior samples
  post_bind(post, out[,na_ind])
}

# apply the function
post = f()

# function to create the plot for one population
plot_f = function(j) {
  est = post_summ(post, sub_index("^E_per_Sa_female[year,pop]$", year = ts_yrs, pop = j))
  plot_tseries(est = est,
               yrs = all_yrs[ts_yrs], label_text = pops[j], y_scale = 1000)

  # add a time series mean
  mn = mean(est["mean",])
  segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])
}

# loop over populations
mypar()
junk = sapply(1:jags_data$nj, plot_f)
axis_labels("Return Year", "Eggs per Female (1000s)")
```
